---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.width = 6,
  fig.height = 5
)
```
Spectroscopy Analysis Tools (spant)
=====

[![Travis Build Status](https://travis-ci.org/martin3141/spant.svg?branch=master)](https://travis-ci.org/martin3141/spant) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/martin3141/spant?branch=master&svg=true)](https://ci.appveyor.com/project/martin3141/spant)
[![](http://cranlogs.r-pkg.org/badges/spant)](http://cran.rstudio.com/web/packages/spant/index.html)
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/spant)](https://cran.r-project.org/package=spant)
[![Coverage Status](https://coveralls.io/repos/github/martin3141/spant/badge.svg?branch=master)](https://coveralls.io/github/martin3141/spant?branch=master)

## Overview
spant provides a full suite of tools to build automated analysis pipelines for
Magnetic Resonance Spectroscopy (MRS) data. The following features are included:

* Raw data import/export.
* Flexible data types to support single voxel, dynamic and spectroscopic imaging data types.
* Publication quality plotting.
* Extensive set of pre-processing steps (phasing, coil-combination, zero-filling, HSVD filtering...)
* Quantum mechanical based simulation for experimental design and basis-set generation.
* Set of metabolite, macromolecule and lipid parameters for typical brain analyses.
* VARPRO based fitting and interfaces for TARQUIN and LCModel for metabolite quantitation.
* Voxel registration to anatomical images for partial volume concentration corrections.

## Installation
You can install the stable version of spant from CRAN:
```{r cran, eval = FALSE}
install.packages("spant", dependencies = TRUE)
```

Or the the development version from GitHub (requires `devtools` package):
```{r github, eval = FALSE}
install.packages("devtools")
devtools::install_github("martin3141/spant")
```

## Documentation
A quick introduction to the basic analysis workflow : https://martin3141.github.io/spant/articles/spant-intro.html

Short tutorials : https://martin3141.github.io/spant/articles/

Function reference : https://martin3141.github.io/spant/reference/