---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.width = 5,
  fig.height = 4
)
```
spant
=====

[![Travis Build Status](https://travis-ci.org/martin3141/spant.svg?branch=master)](https://travis-ci.org/martin3141/spant) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/martin3141/spant?branch=master&svg=true)](https://ci.appveyor.com/project/martin3141/spant)
[![](http://cranlogs.r-pkg.org/badges/spant)](http://cran.rstudio.com/web/packages/spant/index.html)
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/spant)](https://cran.r-project.org/package=spant) 

`muschellij2` badges:
[![Travis Build Status](https://travis-ci.org/muschellij2/spant.svg?branch=master)](https://travis-ci.org/muschellij2/spant)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/muschellij2/spant?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/spant)

## Overview
spant provides a full suite of tools to build automated anaysis pipelines for
Magnetic Resonance Spectroscopy (MRS) data. The following features are included:

* Raw data import/export.
* Flexable data types to support single voxel, dynamic and spectroscopic imaging data types.
* Publication quality plotting.
* Extensive set of pre-processing steps (phasing, coil-combination, zero-filling, HSVD filtering...)
* Quantum mechanical based simulation for experimental design and basis-set generation.
* Set of metabolite, macromolecule and lipid parameters for typical brain analyses.
* VARPRO based fitting and interfaces for TARQUIN and LCModel for metabolite quantitation.
* Voxel registration to anatomical images for partial volume concentration corrections.

## Installation
You can install the stable version of spant from CRAN:
```{r cran, eval = FALSE}
install.packages("spant", dependencies = TRUE)
```

Or the the development version from GitHub (requires `devtools` package):
```{r github, eval = FALSE}
install.packages("devtools")
devtools::install_github("martin3141/spant")
```

## Usage
```{r import, message = FALSE}
library(spant)
fname <- system.file("extdata", "philips_spar_sdat_WS.SDAT", package = "spant")

# import raw data
mrs_data <- read_mrs(fname, format = "spar_sdat")

# output basic data structure
print(mrs_data)

# plot data in the frequency domain
plot(mrs_data, xlim = c(5, 0.5))
```

```{r processing, message = FALSE}
# apply water filter and align to tNAA resonance
mrs_proc <- hsvd_filt(mrs_data)
mrs_proc <- align(mrs_proc, 2.01)
plot(mrs_proc, xlim = c(5, 0.5))
```

```{r basis_sim, message = FALSE}
# simulate a typical basis set for short TE brain analysis
basis <- sim_basis_1h_brain_press(mrs_proc)

# output basis info
print(basis)

# plot basis signals
stackplot(basis, xlim = c(4, 0.5))
```

```{r fitting, message = FALSE}
# perform VARPRO fitting to processed data
fit_res <- fit_mrs(mrs_proc, basis)

# plot the fit estimate, residual and baseline
plot(fit_res, xlim = c(4, 0.5))
```