---
title: "Metabolite simulation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Metabolite simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(ragg)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 5,
  dev = "ragg_png"
)
```

## Simple simulation
Load the spant package:
```{r, message = FALSE}
library(spant)
```

Output a list of pre-defined molecules available for simulation:

```{r, message = FALSE}
get_mol_names()
```

Get and print the spin system for myo-inositol:

```{r, message = FALSE}
ins <- get_mol_paras("ins")
print(ins)
```

Simulate and plot the simulation at 7 Tesla for a pulse acquire sequence
(seq_pulse_acquire), apply 2 Hz line-broadening and plot.
```{r, message = FALSE}
sim_mol(ins, ft = 300e6, N = 4096) %>% lb(2) %>% plot(xlim = c(3.8, 3.1))
```

Other pulse sequences may be simulated including: seq_cpmg_ideal,
seq_mega_press_ideal, seq_press_ideal, seq_slaser_ideal, seq_spin_echo_ideal,
seq_steam_ideal. Note all these sequences assume chemical shift displacement is
negligible. Next we simulate a 30 ms spin-echo sequence and plot:

```{r, message = FALSE}
ins_sim <- sim_mol(ins, seq_spin_echo_ideal, ft = 300e6, N = 4086, TE = 0.03)
ins_sim %>% lb(2) %>% plot(xlim = c(3.8, 3.1))
```

Finally we simulate a range of echo-times and plot all results together to see
the phase evolution:

```{r, message = FALSE, fig.height = 8}
sim_fn <- function(TE) {
  te_sim <- sim_mol(ins, seq_spin_echo_ideal, ft = 300e6, N = 4086, TE = TE)
  lb(te_sim, 2)
}

te_vals <- seq(0, 2, 0.4)

lapply(te_vals, sim_fn) %>% stackplot(y_offset = 150, xlim = c(3.8, 3.1),
                                      labels = paste(te_vals * 100, "ms"))
```

See the [basis simulation](spant-basis-simulation.html) vignette for how to combine these simulations into a basis set for MRS analysis.

## Custom molecules

For simple signals that do not require j-coupling evolution, for example
singlets or approximations to macromolecule or lipid resonances, the
`get_uncoupled_mol` function may be used. In this example we simulated two broad
Gaussian resonances at 1.3 and 1.4 ppm with differing amplitudes:

```{r, message = FALSE}
get_uncoupled_mol("Lip13", c(1.3, 1.4), c("1H", "1H"), c(2, 1), c(10, 10),
                  c(1, 1)) %>% sim_mol %>% plot(xlim = c(2, 0.8))
```

Molecules that aren't defined within spant, or need adjusting to match a particular scan, may be manually defined by constructing a `mol_parameters` object. In the following code we define an imaginary molecule based on Lactate, with the addition of a second spin group containing a singlet at 2.5 ppm. Whilst this molecule could be defined as a single group, it is more computationally efficient to split non j-coupled spin systems up in this way. Note the lineshape is set to a Lorentzian (Lorentz-Gauss factor lg = 0) with a width of 2 Hz. It is generally a good idea to simulate resonances with narrower lineshapes that you expect to see in experimental data, as it is far easier to make a resonance broader than narrower.

```{r, message = FALSE}
nucleus_a <- rep("1H", 4)

chem_shift_a <- c(4.0974, 1.3142, 1.3142, 1.3142)

j_coupling_mat_a <- matrix(0, 4, 4)
j_coupling_mat_a[2,1] <- 6.933
j_coupling_mat_a[3,1] <- 6.933
j_coupling_mat_a[4,1] <- 6.933

spin_group_a <- list(nucleus = nucleus_a, chem_shift = chem_shift_a, 
                     j_coupling_mat = j_coupling_mat_a, scale_factor = 1,
                     lw = 2, lg = 0)

nucleus_b <- c("1H")
chem_shift_b <- c(2.5)
j_coupling_mat_b <- matrix(0, 1, 1)

spin_group_b <- list(nucleus = nucleus_b, chem_shift = chem_shift_b, 
                     j_coupling_mat = j_coupling_mat_b, scale_factor = 3,
                     lw = 2, lg = 0)

source <- "This text should include a reference on the origin of the chemical shift and j-coupling values."

custom_mol <- list(spin_groups = list(spin_group_a, spin_group_b), name = "Cus",
              source = source, full_name = "Custom molecule")

class(custom_mol) <- "mol_parameters"
```

In the next step we output the molecule definition as formatted text and plot it.

```{r, message = FALSE}
print(custom_mol)
custom_mol %>% sim_mol %>% lb(2) %>% zf %>% plot(xlim = c(4.4, 0.5))
```


Once your happy the new molecule is correct, please consider contributing it to the package if you think others would benefit.